Verifying Fine-Grained and Lock-Free Binary Search Trees

### 2022-01-23 concurrency/ITP 2022/Verification of Concurrent Binary Search Tree.tex
ITP 2022 formatting

% !TEX TS-program = pdflatex
% !TEX encoding = UTF-8 Unicode
%% For double-blind review submission
\documentclass[acmsmall,screen]{acmart}\settopmatter{printfolios=true}
%% For single-blind review submission
%\documentclass[acmlarge,review]{acmart}\settopmatter{printfolios=true}
%% For final camera-ready submission
%\documentclass[acmlarge]{acmart}\settopmatter{}

%% Note: Authors migrating a paper from PACMPL format to traditional
%% SIGPLAN proceedings format should change 'acmlarge' to
%% 'sigplan,10pt'.

%% Some recommended packages.
\usepackage{booktabs}   %% For formal tables:
                        %% http://ctan.org/pkg/booktabs
\usepackage{subcaption} %% For complex figures with subfigures/subcaptions
                        %% http://ctan.org/pkg/subcaption

\makeatletter\if@ACM@journal\makeatother
%\acmDOI{10.1145/nnnnnnn.nnnnnnn}
\startPage{1}
\else\makeatother
%% Conference information (used by SIGPLAN proceedings format)
%% Supplied to authors by publisher for camera-ready submission
%\acmDOI{10.1145/nnnnnnn.nnnnnnn}
\startPage{1}
\fi

%% Copyright information
%% Supplied to authors (based on authors' rights management selection;
%% see authors.acm.org) by publisher for camera-ready submission

%% Bibliography style
\bibliographystyle{ACM-Reference-Format}
%% Citation style
%% Note: author/year citations are required for papers published as an
%% issue of PACMPL.
\citestyle{acmauthoryear}   %% For author/year citations

\usepackage{uri}
\usepackage{mathtools}
\usepackage{amsthm}
\usepackage{mathpartir}
\usepackage{semantic}
\usepackage{graphicx}
\usepackage{cases}
\usepackage{hyperref}
\usepackage{stmaryrd}
\usepackage{listings}
\usepackage{iris}
%\usepackage{lstlangcoq}
\usepackage[edges]{forest}
\renewcommand{\lstlistingname}{Figure}

@@

\usepackage[utf8]{inputenc}
\usepackage{geometry}
\geometry{a4paper}

\usepackage{graphicx} % support the \includegraphics command and options
\usepackage{verbatim} % adds environment for commenting out blocks of text & for better verbatim
%\usepackage{amssymb}
\usepackage{url}
\usepackage{listings}

\title{Verifying Fine-Grained and Lock-Free Binary Search Trees}
\author{Roshan Sharma}
\author{Shengyi Wang}
\author{Alexander Oey}
\author{Anastasiia Evdokimova}
\author{Lennart Beringer}
\author{William Mansky}

\date{} % Activate to display a given date or no date (if empty),
         % otherwise the current date is printed

\begin{document}
\acmConference{Some conference}
\maketitle

\catcode`\@=11
\section{Introduction}
\input{intro.tex}

@@

\subsubsection{Key Ranges}
When we traverse the BST looking for a key $k$, we will reach either a node containing $k$, or an empty node where $k$ would appear if it was in the tree. To prove correctness of this procedure, we need ghost state that tracks where each key ``should appear'' in the current tree. As observed by \citet{krishna2017flow}, this can be done by associating each node with a lower and upper bound on the keys appearing in the subtree rooted at that node. We refer to the product of these bounds as a \emph{range}. The range of a node is inherited from its parent, based on the parent's key: if node $n$ has range $(l, r)$ and key $k$, then its left child has range $(l, k)$ and its right child has range $(k, r)$. Figure~\ref{range_bst} shows an example of a BST with each node labeled with its range, starting with $(-\infty, +\infty)$ at the root and propagated to the empty \emph{leaf} nodes. 
\begin{figure}[htb]
\centering
\includegraphics[width=70mm,scale=0.5]{FIG/range_prop.png}
\caption{An example of BST with each node labeled with \emph{range}; lower and upper bound for a key}
\label{range_bst}
\end{figure}
At the leaves, these ranges partition the space of all possible keys. If we reach a leaf node with range $(a, b)$, then we know that keys between $a$ and $b$ 1) are not currently in the tree and 2) can correctly be inserted at this leaf.  For example, suppose we want to insert a key $38$ into the tree in Figure~\ref{range_bst}. The right child of the node with key 35 is a leaf with range $(35, 40)$, so it is guaranteed to be the right place to insert 38.

@@

\begin{figure}[htb]
\centering
\includegraphics[width=150mm,scale=0.5]{FIG/extract_insert.png}
\caption{A visual depiction of the change in global state of BST during $\mathsf{insert(k,v)}$ operation }
\label{extract_insert}
\end{figure}
\begin{figure}[htb]
\centering
\includegraphics[width=150mm,scale=0.5]{FIG/extract_insert_2.png}
\caption{A visual depiction of the change in global state of BST during $\mathsf{insert(k,v)}$ operation, where key $k$ already exists in the tree $t$ }
\label{extract_insert2}
\end{figure}

@@

%% Bibliography
\bibliography{sources}
\end{document}

>>>>

\documentclass[a4paper,USenglish,cleveref, autoref, thm-restate]{lipics-v2021}
%This is a template for producing LIPIcs articles. 
%See lipics-v2021-authors-guidelines.pdf for further information.
%for A4 paper format use option "a4paper", for US-letter use option "letterpaper"
%for british hyphenation rules use option "UKenglish", for american hyphenation rules use option "USenglish"
%for section-numbered lemmas etc., use "numberwithinsect"
%for enabling cleveref support, use "cleveref"
%for enabling autoref support, use "autoref"
%for anonymousing the authors (e.g. for double-blind review), add "anonymous"
%for enabling thm-restate support, use "thm-restate"
%for enabling a two-column layout for the author/affilation part (only applicable for > 6 authors), use "authorcolumns"
%for producing a PDF according the PDF/A standard, add "pdfa"

%\pdfoutput=1 %uncomment to ensure pdflatex processing (mandatatory e.g. to submit to arXiv)
%\hideLIPIcs  %uncomment to remove references to LIPIcs series (logo, DOI, ...), e.g. when preparing a pre-final version to be uploaded to arXiv or another public repository

%\graphicspath{{./graphics/}}%helpful if your graphic files are in another directory

\bibliographystyle{plainurl}% the mandatory bibstyle

\usepackage{txfonts}
\usepackage{subcaption} %% For complex figures with subfigures/subcaptions
                        %% http://ctan.org/pkg/subcaption
\usepackage{uri}
\usepackage{mathtools}
\usepackage{amsthm}
\usepackage{mathpartir}
\usepackage{semantic}
\usepackage{graphicx}
\usepackage{cases}
\usepackage{hyperref}
\usepackage{stmaryrd}
\usepackage{listings}
\usepackage{iris}
%\usepackage{lstlangcoq}
\usepackage[edges]{forest}
\renewcommand{\lstlistingname}{Figure}

@@

\usepackage[utf8]{inputenc}

\title{Verifying Fine-Grained and Lock-Free Binary Search Trees}
\author{Roshan Sharma}{University of Illinois at Chicago, USA}{}{}{}
\author{Shengyi Wang}{Princeton University, USA}{}{}{}
\author{Alexander Oey}{, USA}{}{}{}
\author{Anastasiia Evdokimova}{University of Illinois at Chicago, USA}{}{}{}
\author{Lennart Beringer}{Princeton University, USA}{}{}{}
\author{William Mansky}{University of Illinois at Chicago, USA}{}{}{}

\authorrunning{R. Sharma, S. Wang, A. Oey, A. Evdokimova, L. Beringer, and W. Mansky} %TODO mandatory. First: Use abbreviated first/middle names. Second (only in severe cases): Use first author plus 'et al.'

\Copyright{Roshan Sharma, Shengyi Wang, Alexander Oey, Anastasiia Evdokimova, Lennart Beringer, and William Mansky} %TODO mandatory, please use full first names. LIPIcs license is "CC-BY";  http://creativecommons.org/licenses/by/3.0/

\ccsdesc[100]{\textcolor{red}{Replace ccsdesc macro with valid one}} %TODO mandatory: Please choose ACM 2012 classifications from https://dl.acm.org/ccs/ccs_flat.cfm

\keywords{Dummy keyword} %TODO mandatory; please add comma-separated list of keywords

%\funding{(Optional) general funding statement \dots}%optional, to capture a funding statement, which applies to all authors. Please enter author specific funding statements as fifth argument of the \author macro.

\acknowledgements{I want to thank \dots}%optional

%\nolinenumbers %uncomment to disable line numbering

%Editor-only macros:: begin (do not touch as author)%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\EventEditors{John Q. Open and Joan R. Access}
\EventNoEds{2}
\EventLongTitle{42nd Conference on Very Important Topics (CVIT 2016)}
\EventShortTitle{CVIT 2016}
\EventAcronym{CVIT}
\EventYear{2016}
\EventDate{December 24--27, 2016}
\EventLocation{Little Whinging, United Kingdom}
\EventLogo{}
\SeriesVolume{42}
\ArticleNo{23}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\maketitle

\begin{abstract}
abstract
\end{abstract}

\section{Introduction}
\input{intro.tex}

@@

\subsubsection{Key Ranges}
When we traverse the BST looking for a key $k$, we will reach either a node containing $k$, or an empty node where $k$ would appear if it was in the tree. To prove correctness of this procedure, we need ghost state that tracks where each key ``should appear'' in the current tree. As observed by Krishna et al.~\cite{krishna2017flow}, this can be done by associating each node with a lower and upper bound on the keys appearing in the subtree rooted at that node. We refer to the product of these bounds as a \emph{range}. The range of a node is inherited from its parent, based on the parent's key: if node $n$ has range $(l, r)$ and key $k$, then its left child has range $(l, k)$ and its right child has range $(k, r)$. Figure~\ref{range_bst} shows an example of a BST with each node labeled with its range, starting with $(-\infty, +\infty)$ at the root and propagated to the empty \emph{leaf} nodes. 
\begin{figure}[htb]
\centering
\includegraphics[width=70mm,scale=0.5]{../FIG/range_prop.png}
\caption{An example of BST with each node labeled with \emph{range}; lower and upper bound for a key}
\label{range_bst}
\end{figure}
At the leaves, these ranges partition the space of all possible keys. If we reach a leaf node with range $(a, b)$, then we know that keys between $a$ and $b$ 1) are not currently in the tree and 2) can correctly be inserted at this leaf.  For example, suppose we want to insert a key $38$ into the tree in Figure~\ref{range_bst}. The right child of the node with key 35 is a leaf with range $(35, 40)$, so it is guaranteed to be the right place to insert 38.

@@

\begin{figure}[htb]
\centering
\includegraphics[width=150mm,scale=0.5]{../FIG/extract_insert.png}
\caption{A visual depiction of the change in global state of BST during $\mathsf{insert(k,v)}$ operation }
\label{extract_insert}
\end{figure}
\begin{figure}[htb]
\centering
\includegraphics[width=150mm,scale=0.5]{../FIG/extract_insert_2.png}
\caption{A visual depiction of the change in global state of BST during $\mathsf{insert(k,v)}$ operation, where key $k$ already exists in the tree $t$ }
\label{extract_insert2}
\end{figure}

@@

%% Bibliography
\bibliography{../sources}
\end{document}
